%%% DON'T MODIFY THE PACKAGE IMPORTS & CUSTOMIZATIONS UNLESS YOU REALLY NEED TO ADD ANY PACKAGE %%%
%--------------------------------------------------
% PACKAGES %
%--------------------------------------------------
\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{fontawesome5}
\usepackage{csquotes}
\usepackage{comment}
\usepackage{enumitem}
\usepackage[table,xcdraw]{xcolor}
\usepackage{listings}
\usepackage{authblk}
\usepackage{lipsum}
\usepackage{minitoc}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage[justification=justified]{caption}
\captionsetup{width=\textwidth}
\usepackage{orcidlink}
\usepackage{placeins}
\usepackage{hyperref}
\usepackage{siunitx}
\usepackage{float}
\usepackage{tocloft}
\usepackage{wrapfig}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{bm}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{multirow}

\usepackage[margin=1in]{geometry}
\usepackage{tcolorbox}

\usepackage[version=3]{mhchem}

%--------------------------------------------------
% COLORS & CODE STYLE
%--------------------------------------------------
\definecolor{myblue}{rgb}{0.1, 0.2, 0.6}
\definecolor{mygray}{gray}{0.35}
\definecolor{mygreen}{RGB}{0,120,0}
\definecolor{codebg}{RGB}{248,248,248}
\definecolor{keywordcolor}{RGB}{0,0,180}
\definecolor{stringcolor}{RGB}{153,0,0}
\definecolor{commentcolor}{RGB}{0,128,0}

\lstdefinestyle{bandgap}{
  backgroundcolor=\color{codebg},
  basicstyle=\ttfamily\footnotesize,
  keywordstyle=\color{keywordcolor}\bfseries,
  stringstyle=\color{stringcolor},
  commentstyle=\color{commentcolor}\itshape,
  showstringspaces=false,
  columns=fullflexible,
  keepspaces=true,
  frame=single,
  rulecolor=\color{mygray},
  breaklines=true,
  postbreak=\mbox{\textcolor{mygray}{$\hookrightarrow$}\space},
  language=Python
}

%--------------------------------------------------
% HYPERREF
%--------------------------------------------------
\hypersetup{
    colorlinks=true,
    linkcolor=[RGB]{0,51,153},
    urlcolor=[RGB]{0,51,153},
    citecolor=[RGB]{0,51,153},
    filecolor=[RGB]{0,51,153},
    allcolors=[RGB]{0,51,153}
}

%--------------------------------------------------
% SECTION NUMBERING
%--------------------------------------------------
\renewcommand{\thesection}{\arabic{section}.}
\renewcommand{\thesubsection}{\thesection\arabic{subsection}.}
\renewcommand{\thesubsubsection}{\thesubsection\arabic{subsubsection}.}

\renewcommand\thepart{}
\renewcommand\partname{}
\renewcommand\ptctitle{Table of Contents\\}

%--------------------------------------------------
% ICON SHORTCUTS
%--------------------------------------------------
\newcommand{\github}[1]{\href{#1}{\faGithubSquare}}
\newcommand{\youtube}[1]{\href{#1}{\faYoutubeSquare}}
\newcommand{\database}[1]{\href{#1}{\faDatabase}}

%--------------------------------------------------
% TEAM SUBMISSION ENVIRONMENT
%--------------------------------------------------
\newcounter{teamcount}

\newenvironment{teamsubmission}[2]{
    \clearpage
    \refstepcounter{section}
    \stepcounter{teamcount}
    \addcontentsline{toc}{section}{\theteamcount. #1}
    \begin{center}
        {\LARGE \bfseries #2 \par}
        \vspace{0.25em}
        {\large \textbf{Team:} #1 \par}
    \end{center}
}{
    \FloatBarrier
    \clearpage
}

%--------------------------------------------------
% AUTHORS & AFFILIATIONS
%--------------------------------------------------
\newcommand{\authorsblock}[1]{%
    \begin{center}
        {\normalsize \textbf{#1}\par}
    \end{center}
}

\newcommand{\affiliationsblock}[1]{%
    \begin{center}
        {\textit{#1}\par}
    \end{center}
    \vspace{0.5em}
}

%--------------------------------------------------
% Roman numeral helper (I, II, III, ..., X, L, C, ...)
%--------------------------------------------------
\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}


\begin{document}

%--------------------------------------------------
% TITLE
%--------------------------------------------------
\begin{center}
\parbox{\textwidth}{%
\centering
\LARGE
\setlength{\baselineskip}{1.1\baselineskip}
\textbf{From Knowledge to Action: Outcomes of the 2025 Large Language Model (LLM) Hackathon for Applications in Materials Science and Chemistry}
}
\end{center}


\vspace{0.25em}


% ---------- Global Authors ----------
\input{authors}

\begin{center}
\small
Author names and ORCID identifiers are listed above; institutional affiliations appear in the respective team contributions. Institutional affiliations for authors not associated with a specific team are listed below:\\
Andrew MacBride$^\dagger$ — University of California, Berkeley, California, US.\\
Ben Blaiszik$^*$ — Argonne National Laboratory, Lemont, IL, USA.
\end{center}
\begin{center}
\small
$^*$Corresponding author: Ben Bliaszik (\href{blaiszik@uchicago.edu}{blaiszik@uchicago.edu}).\\$^\dagger$These authors also contributed substantially to compiling team results and other paper writing tasks.
\end{center}


%--------------------------------------------------
% MAIN PAPER CONTENT
%--------------------------------------------------
\begin{abstract}
    In this article, we showcase 88 diverse applications of LLMs in materials science and chemistry as the outcomes from the third Large Language Model (LLM) Hackathon for Applications in Materials Science and Chemistry, engaging more than 275 participants across global hybrid locations. These diverse applications can be generally divided into two high-level categories: i) Knowledge Infrastructure (New ways to know things) and ii) Action Systems (New ways to do things). The appendix contains brief papers for each team submission, with accompanying links to code repositories, video demonstrations, and datasets where applicable. In addition to these team results, we provide a discussion of the hackathon event and its hybrid format, featuring 16 physical hubs distributed across four continents—North America, Europe, Asia, and Australia—complemented by a global online hub that enabled both local and virtual collaboration. Overall, the event revealed substantial advancements in LLM capabilities compared to last two years' hackathons, indicating ongoing expansion of LLM applications in materials science and chemistry research towards the realization of self-driving laboratories. The outcomes illustrate the dual utility of LLMs, serving both as multipurpose models for diverse machine learning tasks and as platforms enabling rapid prototyping of custom scientific applications, while also facilitating the deployment of fully automated workflows across computational and experimental environments. 
\end{abstract}

\section*{Introduction}
Science hackathons have proven to be a compelling tool for encouraging rapid problem-solving in a friendly competitive manner while fostering new collaborations and innovations within the scientific community. Such hackathons can be organized cost-effectively while maximizing both their impact and reach through the utilization of social media, virtual platforms, and hybrid event structures. 

\section*{Overview}
This is the main paper \textbf{Overview} content.

\section*{Conclusion}
This is the main paper \textbf{Conclusion} content.

%--------------------------------------------------
% TABLE OF CONTENTS (AFTER MAIN PAPER)
%--------------------------------------------------
\clearpage
\tableofcontents
\newpage

%--------------------------------------------------
% TEAM SUBMISSIONS (ALL IN ONE FILE)
%--------------------------------------------------
\input{teamsubmissions}

\FloatBarrier
\bibliographystyle{ieeetr}
\bibliography{ref}

\end{document}
